---
title: "linear model from Web"
author: "Alexandra Muoz "
date: ""
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
model.1 =lm(SIMS~ARM, data=data)
abline(model.1)
```



This scatter plot shows simulated strength increases depending on the amount of arm strength exerted by an individual. 


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
This data shows it is moderate positive correlation, between simulated strength and arm strength. 


### Inferential  (Build model.1)

```{r}
summary.lm(model.1)
```

Model 1 shows that the intercept -4.095 and coefficient 0.055 of arm are both of these are both significantly different from zero. 

#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.1, targtPoint, interval = "prediction")
print(predictInt)
```

At Arm=88, Grip=94, the predicted SIMS score is 0.71. 95% confidence interval for that score is SIMS between -1.73 and 3.14.  

#### scatterplot with model fit
  

## Model 2 SIM~GRIP

```{r}
plot(SIMS~GRIP,data=data)
model.2 =lm(SIMS~GRIP, data=data)
abline(model.2)
```

This scatter plot shows simulated strength increases depending on the amount of grip exerted by an individual. 

### Now add in scatterplot




### Numerical results 


```{r}
cor(SIMS~GRIP,data=data)
```
This data shows it is moderate positive correlation = to 0.64 , between simulated strength and grip strength. 

### Inferential  (Build model.2)

```{r}
summary.lm(model.2)
```
  
  Model 1 shows that the intercept -4.81 and coefficient 0.45 of arm are both of these are both significantly different from zero. 

#### predict model.2 at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt = predict(model.2, targtPoint, interval = "prediction")
print(predictInt)
```
At Arm=88, Grip=94, the predicted SIMS score is -0.54. 95% confidence inveral for that score is sims between -3.11 and 2.04. 

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 = lm(SIMS~ARM+GRIP , data=data)
summary(model.3)
```

Both arm and Grip are significantly diffrent from 0 because they are both less than 0.5 

### Numerical results (cor)

```{r}
cor(data)
```
What this shows is that sims corilates with grip ad arm values. 
`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point

```{r}
predict(model.3, targtPoint,interval='prediction')
```
This shows that arm=88, grip= 94, the predictive sims score is 0.15. At that score the 95% confidence interval is sims between -2.13 ans 2.43. 
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova_result <- anova(model.1, model.3)
print(anova_result)
```
Model 2 is bettter than model 1 because the p value for comparison is less than 0.05. 

```{r}
anova_result <- anova(model.2, model.3)
print(anova_result)
```


